### 2013-09-18 chi2014/results.tex
hypothesis 3 test

>>>>

\subsubsection{Hypothesis 3}

This interpretation supports \textbf{Hypothesis 3:} There is a set of general, common ideas that make up the first several responses of every crowd brainstorming session, regardless of condition. We test this interpretation by constructing a set of the top 66 (5\%) most common ideas. If our intuition is correct, these ideas should be more likely to appear in the first 5 instances of a run than they are to appear in any of the following instances. We designate two Bernoulli variables. The first, defined by parameter $\theta_f$, represents the probability that an instance is in the common set given it is in the first five instances of a run. The second, defined by parameter $\theta_l$, is the probability that an instance is in the common pool given it is one of the \emph{last} (>5) instances in a run..

We fit these parameters using data from all runs with a total number of instances greater than 10. We chose this so that no run could contribute evidence to $\theta_f$ without also contributing to $\theta_l$. The resulting parameters were $\theta_f = 0.564$ (95\% HDI 0.517-0.611) and $\theta_l = 0.323$ (95\% HDI 0.303-0.342). This difference is significant, supporing the hypothesis that common ideas are over-represented in the early part of a brainstorming run, regardless of conditon.
